---
title: "Conspiracy_values_trust"
output: html_document
date: "2023-07-08"
---


db: https://ess-search.nsd.no/en/study/172ac431-2a06-41df-9dab-c1fd8f3877e7


# Work outline:
* LIBRARIES
* DB UPLOAD
* DB CLEANING & EXPLORATORY ANALYSIS
    - keep only var of interest
    - correcting NA
    - variables selection
    - re-coding variables
    - dependent var merge
    - plot variables freq
    - variables normalization
    - dummy encoding
    - correlation matrix
* PCA
    - PCA for human values
    - EFA for human values
    - PCA for trust var
    - EFA for trust var
    - PCA correlaion matrix
* REGRESSION
    - conspiracy model
    - stepwise selection
    - multicollinearity test
    - secgrdec model
    - stepwise selection
    - multicollinearity test
    - scidecpb model
    - stepwise selection
    - multicollinearity test
[Other models]
  




### Libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tibble)
library(survey)
library(ggcorrplot)
library(psych)
library(MASS)
library(ltm)
library(caret)
library(fastDummies)
library(glmnet)
library(tidyr)
library(sjPlot)
```



### DB uploads
```{r}
df <- read_csv("dataset/original/ESS10.csv")

```

# DB CLEANING

Removing countries other than IT
```{r}
df <- df %>% 
  filter(cntry == "IT")

```

```{r}
head(df)
```




## Possible columns of interest
```{r}
cols_to_keep <- c(
  # ID & WEIGHTS
  "idno",       # Respondent's identification number
  "dweight",    # Design weight
  "pspwght",    # Post-stratification weight including design weight
  "pweight",    # Population size weight 
  "anweight",   # Analysis weight
  # MEDIA & SOCIAL TRUST
  "nwspol",     # News about politics and curren ... ading or listening, in minutes
  "netustm",    # Internet use, how much time on typical day, in minutes
  "ppltrst",    # Most people can be trusted or you can't be too careful
  # POLITICS & TRUST
  "polintr",    # How interested in politics
  "trstlgl",    # Trust in the legal system
  "trstplc",    # Trust in the police
  "trstplt",    # Trust in politicians
  "trstep",     # Trust in the European Parliament
  "trstsci",    # Trust in scientists
  "vote",       # Voted last national election
  "prtvtdit",   # Party voted for in last national election, Italy
  "pbldmna",    # Taken part in public demonstration last 12 months
  "lrscale",    # Placement on left right scale
  "stflife",    # How satisfied with life as a whole
  "stfgov",     # How satisfied with the national government
  "freehms",    # Gays and lesbians free to live life as they wish
  "euftf",      # European Union: European unification go further or gone too far
  "imwbcnt",    # Immigrants make country worse or better place to live
  # WELL-BEING, RELIGION & ETNICITHY
  "happy",      # How happy are you (check w/ satlife)
  "sclmeet",    # How often socially meet with friends, relatives or colleagues
  "health",     # Subjective general health
  "rlgblg",     # Belonging to particular religion or denomination
  "rlgdnm",     # Religion or denomination belonging to at present (which one)
  "dscrgrp",    # Member of a group discriminated against in this country
  "ctzcntr",    # Citizen of country
  "brncntr",    # Born in country
  "cntbrthd",   # Country of birth
  "wrclmch",    # How worried about climate change
  "vteurmmb",   # Would vote for IT to stay a  member of European Union or leave
  # UNDERSTANDING OF DEMOCRACY
  "viepolc",    # In IT the views of ordina ... e views of the political elite
  "keydecc",    # In country key decisions are m ... rather than the European Union
  "accalaw",    # Acceptable for country to have a strong leader above the law
  # GENDER, AGE & HOUSEHOLD
  "hhmmb",      # Number of people living regularly as member of household
  "gndr",       # Gender
  "agea",       # Age of respondent, calculated
  # SOCIO-DEMOGRAPHICS
  "marsts",     # Legal marital status
  "chldhhe",    # Ever had children living in household
  "domicil",    # Domicile, respondent's description
  "edlveit",    # Highest level of education, Italy
  "mnactic",    # Main activity last 7 days, all respondents
  "emplrel",    # Employment relation
  "hincfel",    # Feeling about household's income nowadays
  "edlvpeit",   # Partner's highest level of education, Italy
  "edlvfeit",   # Father's highest level of education, Italy
  "edlvmeit",   # Mother's highest level of education, Italy
  "region",     # Region
  # DIGITAL SOCIAL CONTACTS
  "mcmsinf",    # Online/mobile communication exposes people to misinformation
  "stfmjob",    # How satisfied are you in your main job
  "c19wplch",   # Work place change occurred as a result of COVID-19
  # HUMAN VALUES
  "ipcrtiv",    # Important to think new ideas and being creative
  "imprich",    # Important to be rich, have money and expensive things
  "ipeqopt",    # Important that people are trea ... y and have equal opportunities
  "ipshabt",    # Important to show abilities and be admired
  "impsafe",    # Important to live in secure and safe surroundings
  "impdiff",    # Important to try new and different things in life
  "ipfrule",    # Important to do what is told and follow rules
  "ipudrst",    # Important to understand different people
  "ipmodst",    # Important to be humble and modest, not draw attention
  "ipgdtim",    # Important to have a good time
  "impfree",    # Important to make own decisions and be free
  "iphlppl",    # Important to help people and care for others well-being
  "ipsuces",    # Important to be successful and that people recognize achievements
  "ipstrgv",    # Important that government is strong and ensures safety
  "ipadvnt",    # Important to seek adventures and have an exciting life
  "ipbhprp",    # Important to behave properly
  "iprspot",    # Important to get respect from others
  "iplylfr",    # Important to be loyal to friends and devote to people close
  "impenv",     # Important to care for nature and environment
  "imptrad",    # Important to follow traditions and customs
  "impfun",     # Important to seek fun and things that give pleasure
  # COVID-19
  "secgrdec",   # Small secret group of people r ... or decisions in world politics
  "scidecpb",   # Groups of scientists manipulat ... in order to deceive the public
  "panfolru",   # More important to follow gover ... sions when fighting a pandemic
  "gvhanc19",   # How satisfied with government's handling of COVID-19 in IT
  "gvconc19",   # COVID-19 is result of delibera ... ome government or organisation
  "respc19",    # Respondent had COVID-19
  "reshhc19",   # Anyone living with respondent had COVID-19
  "getavc19"   # Whether respondent will get vax ... egulatory authority in country
)

df <- dplyr::select(df, all_of(cols_to_keep))

```



# SUBSTITUTING 7/8/9 VALUES WITH  NA

### Populating NA for the values 7/8/9 in Human values
```{r}
var_hum_values <- c("ipcrtiv", "imprich", "ipeqopt", "ipshabt", "impsafe", 
                    "impdiff", "ipfrule", "ipudrst", "ipmodst", "ipgdtim",
                    "impfree", "iphlppl", "ipsuces", "ipstrgv", "ipadvnt", 
                    "ipbhprp", "iprspot", "iplylfr", "impenv", "imptrad", 
                    "impfun")



df <- df %>%
  mutate(across(all_of(var_hum_values), ~ifelse(. %in% c(7, 8, 9), NA, .)))
```


### Populating NA for the other values 7/8/9
```{r}
variable_names <- c("polintr", "vote", "pbldmna", "freehms", "health", 
                    "rlgblg", "dscrgrp", "ctzcntr", "brncntr", "gndr", 
                    "domicil", "hincfel", "secgrdec", "scidecpb", "gvconc19", 
                    "respc19", "reshhc19")



df <- df %>%
  mutate(across(all_of(variable_names), ~ifelse(. %in% c(7, 8, 9), NA, .)))
```


### Populating NA for the values 6/7/8/9
```{r}
variable_names <- c("wrclmch", "chldhhe", "emplrel", "c19wplch", "getavc19")


df <- df %>%
  mutate(across(all_of(variable_names), ~ifelse(. %in% c(6, 7, 8, 9), NA, .)))
```


### Populating NA for the values 77/88/99 
```{r}
variable_names <- c("ppltrst", "trstlgl", "trstplc", "trstplt", "trstep", 
                    "trstsci", "lrscale", "stflife", "stfgov", "euftf", 
                    "imwbcnt", "happy", "sclmeet", "vteurmmb", "viepolc", 
                    "keydecc", "accalaw", "hhmmb", "mcmsinf", "panfolru", 
                    "gvhanc19")


df <- df %>%
  mutate(across(all_of(variable_names), ~ifelse(. %in% c(77, 88, 99), NA, .)))
```


### Populating NA for the values 66/77/88/99
```{r}
variable_names <- c("prtvtdit", "rlgdnm", "marsts", "mnactic", "stfmjob")


df <- df %>%
  mutate(across(all_of(variable_names), ~ifelse(. %in% c(66, 77, 88, 99), NA, .)))
```


### Populating NA for the values 777/888/999
```{r}
variable_names <- c("agea")


df <- df %>%
  mutate(across(all_of(variable_names), ~ifelse(. %in% c(777, 888, 999), NA, .)))
```


### Populating NA for the values 6666/7777/8888/9999
```{r}
variable_names <- c("nwspol", "netustm", "cntbrthd", "edlveit", "edlvpeit", 
                    "edlvfeit", "edlvmeit")


df <- df %>%
  mutate(across(all_of(variable_names), ~ifelse(. %in% c(6666, 7777, 8888, 9999), NA, .)))
```


## FINAL VARIABLES KEPT
```{r}
cols_to_keep <- c(
  # DEPENDENT VARIABLES
  "secgrdec",   # Small secret group of people r ... or decisions in world politics
  "scidecpb",   # Groups of scientists manipulat ... in order to deceive the public
  
  # CONTROL VARIABLES
  "nwspol",     # News about politics and curren ... ading or listening, in minutes
  "pbldmna",    # Taken part in public demonstration last 12 months
  "stflife",    # How satisfied with life as a whole
  "sclmeet",    # How often socially meet with friends, relatives or colleagues
  "hhmmb",      # Number of people living regularly as member of household
  "gndr",       # Gender
  "agea",       # Age of respondent, calculated
  "polintr",    # How interested in politics  
  "domicil",    # Domicile, respondent's description
  "edlveit",    # Highest level of education, Italy
  "hincfel",    # Feeling about household's income nowadays
  "mcmsinf",    # Online/mobile communication exposes people to misinformation
  "panfolru",   # More important to follow gover ... sions when fighting a pandemic
  "gvhanc19",   # How satisfied with government's handling of COVID-19 in IT
  "respc19",    # Respondent had COVID-19
  "reshhc19",   # Anyone living with respondent had COVID-19
  "getavc19",   # Whether respondent will get vax ... egulatory authority in country
  
  # TRUST IN THE ESTABLISHMENT 
  "ppltrst",    # Most people can be trusted or you can't be too careful
  "trstlgl",    # Trust in the legal system
  "trstplc",    # Trust in the police
  "trstplt",    # Trust in politicians
  "trstep",     # Trust in the European Parliament
  "trstsci",    # Trust in scientists
  "viepolc",    # In IT the views of ordina ... e views of the political elite
  

  # HUMAN VALUES
  "ipcrtiv",    # Important to think new ideas and being creative
  "imprich",    # Important to be rich, have money and expensive things
  "ipeqopt",    # Important that people are trea ... y and have equal opportunities
  "ipshabt",    # Important to show abilities and be admired
  "impsafe",    # Important to live in secure and safe surroundings
  "impdiff",    # Important to try new and different things in life
  "ipfrule",    # Important to do what is told and follow rules
  "ipudrst",    # Important to understand different people
  "ipmodst",    # Important to be humble and modest, not draw attention
  "ipgdtim",    # Important to have a good time
  "impfree",    # Important to make own decisions and be free
  "iphlppl",    # Important to help people and care for others well-being
  "ipsuces",    # Important to be successful and that people recognize achievements
  "ipstrgv",    # Important that government is strong and ensures safety
  "ipadvnt",    # Important to seek adventures and have an exciting life
  "ipbhprp",    # Important to behave properly
  "iprspot",    # Important to get respect from others
  "iplylfr",    # Important to be loyal to friends and devote to people close
  "impenv",     # Important to care for nature and environment
  "imptrad",    # Important to follow traditions and customs
  "impfun"     # Important to seek fun and things that give pleasure
)

df <- df %>% 
  dplyr::select(all_of(cols_to_keep))


```


# checking the 5555 in edlveit
```{r}
count_5555 <- sum(df$edlveit == 5555)
count_5555
df <- df[df$edlveit != 5555, ]
```

### na drop
```{r}
na_percentages <- colSums(is.na(df)) / nrow(df) * 100
na_percentages
```

```{r}
df <- na.omit(df)
```


```{r}
summary(df)
```



# RECODING

### Human Values
```{r}
df[var_hum_values] <- lapply(df[var_hum_values], function(x) {
  ifelse(x %in% c(1, 2, 3, 4, 5, 6), 7 - x, x)
})

```


### Control Variables
```{r}
var_contr <- c("nwspol", "stflife", "sclmeet", "hhmmb", "agea", 
               "polintr", "domicil", "edlveit", "hincfel", "mcmsinf",
               "panfolru", "gvhanc19")

var_contr_D <- c("pbldmna", "gndr", "respc19", "reshhc19", "getavc19")
```


```{r}
df[c("polintr", "hincfel")] <- lapply(df[c("polintr", "hincfel")], function(x) {
  ifelse(x %in% c(1, 2, 3, 4), 5 - x, x)
})

```

```{r}
df$domicil <- 6 - df$domicil # how big the city you live in
df$panfolru <- 10 - df$panfolru # would you follow government rules
```

```{r}
# collapse then change: 0 = no, 1 = yes
df$respc19 <- ifelse(df$respc19 < 3, 1, 0)
df$getavc19 <- ifelse(df$getavc19 < 3, 1, 0)
df$reshhc19 <- ifelse(df$reshhc19 < 3, 1, 0)

```

```{r}
df$pbldmna <- ifelse(df$pbldmna == 2, 0, df$pbldmna)
df$gndr <- ifelse(df$gndr == 2, 0, df$gndr) # male
```


### Dependent variables
```{r}
df[c("secgrdec", "scidecpb")] <- lapply(df[c("secgrdec", "scidecpb")], function(x) {
  ifelse(x %in% c(1, 2, 3, 4, 5), 6 - x, x)
})
```




## Merge the 2 dependent variable into one
```{r}
# merge the dependent variable (different approach analyzed later)
df$consprcy <- rowMeans(df[c("secgrdec", "scidecpb")],na.rm=T); 

```

## Alpha cronbach consistency 
```{r}
cronbach.alpha(df[c("secgrdec", "scidecpb")]) # alpha acceptable since > 0.7
```


# Plot histograms

```{r}
plotVariableFrequencies <- function(data, variables) {
  for (variable in variables) {
    freq_table <- table(data[[variable]])
    
    barplot(freq_table, main = paste("Frequency Plot of", variable),
            xlab = variable, ylab = "Frequency")
    
    file_name <- paste0("plots/", variable, ".png")
    png(file_name)
    barplot(freq_table, main = paste("Frequency Plot of", variable),
            xlab = variable, ylab = "Frequency")
    dev.off()
  }
}

```



dependent variables
```{r}
var_dep <- c("secgrdec", "scidecpb", "consprcy")
```

```{r}
sumstat_dep <- summary(df[c("secgrdec", "scidecpb", "consprcy")]); sumstat_dep

plotVariableFrequencies(df, c("secgrdec", "scidecpb", "consprcy"))

```


human values
```{r}
sumstat_val <- summary(df[var_hum_values]); sumstat_val

plotVariableFrequencies(df, var_hum_values)
```


trust variables
```{r}
var_trust <-  c("ppltrst", "trstlgl", "trstplc", "trstplt", "trstep", 
                "trstsci", "viepolc")    
```

```{r}
sumstat_tr <- summary(df[var_trust]); sumstat_tr

plotVariableFrequencies(df, var_trust)
```

control variables
```{r}
sumstat_cont <- summary(df[var_contr]); sumstat_cont

plotVariableFrequencies(df, var_contr)
```

```{r}
computeDummyVariableFrequencies <- function(data, dummy_variables) {
  frequencies <- lapply(dummy_variables, function(variable) {
    freq_table <- table(data[[variable]])
    rel_freq_table <- prop.table(freq_table)
    result <- data.frame(Dummy_Variable = variable, Frequency = freq_table, Relative_Frequency = rel_freq_table)
    return(result)
  })
  
  return(frequencies)
}

```

```{r}
computeDummyVariableFrequencies(df, var_contr_D)
```




# RESCALING (Variable normalization)

### Human Values
```{r}
df[var_hum_values] <- df[var_hum_values] %>% 
  scale()
```

### Trust
```{r}
df[var_trust] <- df[var_trust] %>% 
  scale()
```

### Control variables 
```{r}
df[var_contr] <- df[var_contr] %>% 
  scale()
```

### Dummy Encoding
```{r}
df_dummies <- dummyVars(~., data = df[var_contr_D])
df_dummies <- predict(df_dummies, newdata = df[var_contr_D])
df <- cbind(df[!names(df) %in% var_contr_D], df_dummies)

df <- as_tibble(df)
```

### Dependent variables
```{r}
df[c("secgrdec", "scidecpb", "consprcy")] <- df[c("secgrdec", "scidecpb", "consprcy")] %>% 
  scale()
```





# CORRELATION

### Human Values
```{r}
cor_hum_val <- df[var_hum_values] %>% 
  cor()

round(cor_hum_val, 2)
```
```{r}
col<- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(x = cor_hum_val, col = col, symm = TRUE, Colv = NA, Rowv = NA, 
        main = "Heatmap Human values")
```



### Trust
```{r}
cor_trust <- df[var_trust] %>% 
  cor()

round(cor_trust, 2)
```


## Correlation all variables
```{r}
cor_matr <- df[!names(df) %in% var_contr_D] %>%
  cor()


round(cor_matr, 2)
```

# dependent variables
```{r}
cor_dep <- df[var_dep] %>% 
  cor()

round(cor_dep, 2)
```



# PCA

### Human values

```{r}
subset_hum_val <- df[var_hum_values]
```


```{r}
fa.parallel(subset_hum_val, fa='pc', show.legend=FALSE, main = "Parallel analysis: Human values")

output_file <- "plot_pca_hum.png"

png(filename = output_file)
fa.parallel(subset_hum_val, fa='pc', show.legend=FALSE, main = "Parallel analysis: Human values")
dev.off()
```


```{r}
pc_val <- principal(subset_hum_val, nfactors=4, rotate = 'varimax', scores = T, missing = T)
pc_val
```

```{r}
head(pc_val$scores)

round(unclass(pc_val$weights), 2)
```

### EFA Human Values
```{r}
# EFA
fa.parallel(subset_hum_val, fa='both', show.legend=FALSE, main = "Scree plot with parallel analysis")
```

```{r}
fa_val <- fa(subset_hum_val, nfactors = 4, rotate = 'varimax', scores = T, fm = "minres")
fa_val
```

```{r}
fa.diagram(fa_val, simple = T)
```

### Trust
```{r}
subset_trust <- df[var_trust]
```

```{r}
fa.parallel(subset_trust, fa='pc', show.legend=FALSE, main = "Scree plot with parallel analysis")

output_file <- "plot_pca_tr.png"

png(filename = output_file)
fa.parallel(subset_trust, fa='pc', show.legend=FALSE, main = "Scree plot: trust")
dev.off()

```

```{r}
pc_tr <- principal(subset_trust, nfactors=2, rotate = 'varimax', scores = T, missing = T)
pc_tr
```

```{r}
head(pc_tr$scores)

round(unclass(pc_tr$weights), 2)
```


### EFA Trust
```{r}
# EFA
fa.parallel(subset_trust, fa='both', show.legend=FALSE, main = "Scree plot with parallel analysis")
```

```{r}
fa_tr <- fa(subset_trust, nfactors = 2, rotate = 'varimax', scores = T, fm = "minres")
fa_tr
```

```{r}
fa.diagram(fa_tr, simple = F)
```

Add PCs to df
```{r}
df$rc1_val <- pc_val$scores[, 1]
df$rc2_val <- pc_val$scores[, 2]
df$rc3_val <- pc_val$scores[, 3]
df$rc4_val <- pc_val$scores[, 4]

df$rc1_tr <- pc_tr$scores[, 1]
df$rc2_tr <- pc_tr$scores[, 2]

```


# Correlations with RC
```{r}
df_slim_noD <- df[c(var_dep, "rc1_val", "rc2_val", "rc3_val",
                "rc4_val", "rc1_tr", "rc2_tr", var_contr)]
```

```{r}
cor_matr_rc <- df_slim_noD %>% 
  cor()

round(cor_matr_rc, 2)
```

```{r}
col<- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(cor_matr_rc, col = col, symm = TRUE, Colv = NA, Rowv = NA,
        main = "Correlation heatmap")

```


### Remove from df human values and trust variables

```{r}
df_slim = NULL
df_slim <- df[c(var_dep, "rc1_val", "rc2_val", "rc3_val",
                "rc4_val", "rc1_tr", "rc2_tr", var_contr, var_contr_D)]
```





# REGRESSION


## predicting consprcy
```{r}
lm_m0 <- lm(consprcy ~ . - scidecpb - secgrdec  , data = df_slim)
summary(lm_m0)
```

### VIF test 
```{r}
car::vif(lm_m0) 
```
no multicollinearity


### Stepwise selection
```{r}
stepAIC(lm_m0, direction = "both")
```

```{r}
lm_m1 <- lm(formula = consprcy ~ rc1_val + rc2_val + rc3_val + rc1_tr + 
    rc2_tr + sclmeet + agea + polintr + domicil + hincfel + mcmsinf + 
    panfolru + gvhanc19 + gndr + getavc19, data = df_slim)
summary(lm_m1)

tab_model(lm_m1)
```

multicollinearity test
```{r}
car::vif(lm_m1) # no collinearity problem detectded
```





## Predict secgrdec

```{r}
lm_g0 <- lm(secgrdec ~ . - scidecpb - consprcy, data = df_slim)
summary(lm_g0)
```

### VIF test 
```{r}
car::vif(lm_g0) # no multicoll. problems
```

### Stepwise selection
```{r}
stepAIC(lm_g0, direction = "both")
```

```{r}
lm_g1 <- lm(formula = secgrdec ~ rc1_val + rc2_val + rc1_tr + sclmeet + 
    domicil + hincfel + panfolru + gvhanc19 + getavc19, data = df_slim)

summary(lm_g1)
tab_model(lm_g1)
```


## Predict scidecpb

```{r}
lm_s0 <- lm(scidecpb ~ . - secgrdec - consprcy, data = df_slim)
summary(lm_s0)
```

### VIF test 
```{r}
car::vif(lm_s0) # no multicoll. problems
```

### Stepwise selection
```{r}
stepAIC(lm_s0, direction = "both")
```

```{r}
lm_s1 <- lm(formula = scidecpb ~ rc2_val + rc3_val + rc1_tr + rc2_tr + 
    sclmeet + agea + polintr + edlveit + hincfel + mcmsinf + 
    panfolru + gvhanc19 + gndr + respc19 + getavc19, data = df_slim)
summary(lm_s1)
tab_model(lm_s1)
```
This one has the highest R-squared so far



# OTHER MODELS

## Lasso regression for consprcy
```{r}
y <- df_slim$consprcy
x <- data.matrix(df_slim[, c("rc1_val",  "rc2_val",  "rc3_val",  "rc4_val", 
                           "rc1_tr",   "rc2_tr",   "nwspol",   "stflife", 
                           "sclmeet",  "hhmmb", "agea", "polintr",  "domicil",  
                           "edlveit",  "hincfel",  "mcmsinf",  "panfolru",
                           "gvhanc19", "pbldmna",  "gndr", "respc19", 
                           "reshhc19", "getavc19")])

```

```{r}
cv_model <- cv.glmnet(x, y, alpha = 1)

best_lambda <- cv_model$lambda.min
best_lambda

plot(cv_model)
```

```{r}
best_model <- glmnet(x, y, alpha = 1, lambda = best_lambda)
coef(best_model)
```




## Lasso regression for scidecpb
```{r}
y <- df_slim$scidecpb
x <- data.matrix(df_slim[, c("rc1_val",  "rc2_val",  "rc3_val",  "rc4_val", 
                           "rc1_tr",   "rc2_tr",   "nwspol",   "stflife", 
                           "sclmeet",  "hhmmb", "agea", "polintr",  "domicil",  
                           "edlveit",  "hincfel",  "mcmsinf",  "panfolru",
                           "gvhanc19", "pbldmna",  "gndr", "respc19", 
                           "reshhc19", "getavc19")])

```

```{r}
cv_model <- cv.glmnet(x, y, alpha = 1)

best_lambda <- cv_model$lambda.min
best_lambda

plot(cv_model)
```
```{r}
best_model <- glmnet(x, y, alpha = 1, lambda = best_lambda)
coef(best_model)
```

```{r}
best_model <- glmnet(x, y, alpha = 1, lambda = best_lambda)
coef(best_model)
```










## Ridge regression for consprcy
```{r}
y <- df_slim$consprcy
x <- data.matrix(df_slim[, c("rc1_val",  "rc2_val",  "rc3_val",  "rc4_val", 
                           "rc1_tr",   "rc2_tr",   "nwspol",   "stflife", 
                           "sclmeet",  "hhmmb", "agea", "polintr",  "domicil",  
                           "edlveit",  "hincfel",  "mcmsinf",  "panfolru",
                           "gvhanc19", "pbldmna",  "gndr", "respc19", 
                           "reshhc19", "getavc19")])

```

```{r}
cv_model <- cv.glmnet(x, y, alpha = 0)

best_lambda <- cv_model$lambda.min
best_lambda

plot(cv_model)
```

```{r}
best_model <- glmnet(x, y, alpha = 0, lambda = best_lambda)
coef(best_model)
```





## Ridge regression for scidecpb
```{r}
y <- df_slim$scidecpb
x <- data.matrix(df_slim[, c("rc1_val",  "rc2_val",  "rc3_val",  "rc4_val", 
                           "rc1_tr",   "rc2_tr",   "nwspol",   "stflife", 
                           "sclmeet",  "hhmmb", "agea", "polintr",  "domicil",  
                           "edlveit",  "hincfel",  "mcmsinf",  "panfolru",
                           "gvhanc19", "pbldmna",  "gndr", "respc19", 
                           "reshhc19", "getavc19")])

```

```{r}
cv_model <- cv.glmnet(x, y, alpha = 0)

best_lambda <- cv_model$lambda.min
best_lambda

plot(cv_model)
```

```{r}
best_model <- glmnet(x, y, alpha = 0, lambda = best_lambda)
coef(best_model)
```










